---
title: "Scrape Covid-19 Cases Data & its Visual Representation in Malaysia with Python & R"
output: html_notebook
---

# Check out my COVID Analysis

This is the approach I used. I got the data from this source: [data.humdata](https://data.humdata.org/dataset/novel-coronavirus-2019-ncov-cases)

# Import data

This is where we import data.

```{r}

library(tidyverse)

covid19_confirmed_malaysia_raw <- read_csv("https://data.humdata.org/hxlproxy/api/data-preview.csv?url=https%3A%2F%2Fraw.githubusercontent.com%2FCSSEGISandData%2FCOVID-19%2Fmaster%2Fcsse_covid_19_data%2Fcsse_covid_19_time_series%2Ftime_series_covid19_confirmed_global.csv&filename=time_series_covid19_confirmed_global.csv")

```

# Load Libraries
```{r}
library(tidyverse)
library(lubridate)
```

# Graph of Confirmed COVID-19 cases in Malaysia
```{r}
theme_set(theme_minimal())

covid19_confirmed_malaysia <- covid19_confirmed_malaysia_raw %>%
  pivot_longer(-c(`Province/State`, `Country/Region`, Lat, Long),
               names_to = "date",
               values_to = "confirmed_n"
  ) %>%
  select(-c(Lat, Long)) %>%
  rename(
    province_state = `Province/State`,
    country_region = `Country/Region`
  ) %>%
  mutate(date = mdy(date)) %>%
  group_by(country_region, date) %>%
  summarise(confirmed_n = sum(confirmed_n)) %>%
  ungroup()

covid19_confirmed_malaysia %>%
  arrange(date) %>%
  group_by(country_region) %>% 
  mutate(new_confirmed_cases = confirmed_n - lag(confirmed_n, default = 0)) %>%
  ungroup() %>% 
  filter(country_region == "Malaysia") %>%
  ggplot(aes(x = date, y = new_confirmed_cases)) +
  geom_line() +
  scale_x_date(date_breaks = "5 weeks", date_labels = "%d %b") +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "Date", y = "New Cases", title = "New Confirmed COVID-19 cases in Malaysia")


```

# Import data

This is where we import data.

```{r}

covid19_death_malaysia_raw <- read_csv("https://data.humdata.org/hxlproxy/api/data-preview.csv?url=https%3A%2F%2Fraw.githubusercontent.com%2FCSSEGISandData%2FCOVID-19%2Fmaster%2Fcsse_covid_19_data%2Fcsse_covid_19_time_series%2Ftime_series_covid19_deaths_global.csv&filename=time_series_covid19_deaths_global.csv")

```

# Load Libraries
```{r}
library(tidyverse)
library(lubridate)
```

# Graph of Death COVID-19 cases in Malaysia
```{r}
theme_set(theme_minimal())

covid19_death_malaysia <- covid19_death_malaysia_raw %>%
  pivot_longer(-c(`Province/State`, `Country/Region`, Lat, Long),
               names_to = "date",
               values_to = "death_n"
  ) %>%
  select(-c(Lat, Long)) %>%
  rename(
    province_state = `Province/State`,
    country_region = `Country/Region`
  ) %>%
  mutate(date = mdy(date)) %>%
  group_by(country_region, date) %>%
  summarise(death_n = sum(death_n)) %>%
  ungroup()

covid19_death_malaysia %>%
  arrange(date) %>%
  group_by(country_region) %>% 
  mutate(new_death_cases = death_n - lag(death_n, default = 0)) %>%
  ungroup() %>% 
  filter(country_region == "Malaysia") %>%
  ggplot(aes(x = date, y = new_death_cases)) +
  geom_line() +
  scale_x_date(date_breaks = "5 weeks", date_labels = "%d %b") +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "Date", y = "New Death Cases", title = "New Death COVID-19 cases in Malaysia")


```

# Import data

This is where we import data.

```{r}

covid19_recovered_malaysia_raw <- read_csv("https://data.humdata.org/hxlproxy/api/data-preview.csv?url=https%3A%2F%2Fraw.githubusercontent.com%2FCSSEGISandData%2FCOVID-19%2Fmaster%2Fcsse_covid_19_data%2Fcsse_covid_19_time_series%2Ftime_series_covid19_recovered_global.csv&filename=time_series_covid19_recovered_global.csv")

```

# Load Libraries
```{r}
library(tidyverse)
library(lubridate)
```

# Graph of Recovered COVID-19 cases in Malaysia
```{r}
theme_set(theme_minimal())

covid19_recovered_malaysia <- covid19_recovered_malaysia_raw %>%
  pivot_longer(-c(`Province/State`, `Country/Region`, Lat, Long),
               names_to = "date",
               values_to = "recovered_n"
  ) %>%
  select(-c(Lat, Long)) %>%
  rename(
    province_state = `Province/State`,
    country_region = `Country/Region`
  ) %>%
  mutate(date = mdy(date)) %>%
  group_by(country_region, date) %>%
  summarise(recovered_n = sum(recovered_n)) %>%
  ungroup()

covid19_recovered_malaysia %>%
  arrange(date) %>%
  group_by(country_region) %>% 
  mutate(new_recovered_cases = recovered_n - lag(recovered_n, default = 0)) %>%
  ungroup() %>% 
  filter(country_region == "Malaysia") %>%
  ggplot(aes(x = date, y = new_recovered_cases)) +
  geom_line() +
  scale_x_date(date_breaks = "5 weeks", date_labels = "%d %b") +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "Date", y = "New Recovered Cases", title = "New Recovered COVID-19 cases in Malaysia")


```

